---
title: "Mini-Project 3"
author: "Emily Liu, Karina Lieb, and Alexis Kilayko"
date: "April 14, 2018"
output: 
  html_document:
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
# Loading libraries
library(tidyverse)
library(leaflet)
library(macleish)
library(sf)
library(mapview)
```

```{r, eval = FALSE}
# Downloading contour data, not needed after it was added to GitHub. 
# url <- "http://download.massgis.digital.mass.gov/shapefiles/state/contours250k.zip"
# local_file <- basename(url)
# download.file(url, destfile = local_file)
# unzip(local_file, exdir = "contours250k")
# dsn <- path.expand("contours250k")
# dsn
# list.files(dsn)
# contours <- read_sf(dsn)
# Limiting contour data to within Macleish area
# contours_4326 <- contours %>%
#   st_transform(4326)
# contours_inside <- macleish_layers[["boundary"]] %>%
#   st_intersection(contours_4326)
```

```{r}
# AEA projection scheme for buffers
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```

```{r}
# Create current campsite points
campsites_pt <- tribble(
  ~point, ~lat, ~lon,
  "Group Campsite", -72.678154, 42.450976,
  "Remote Campsite", -72.679581, 42.458549
)

# Convert campsite points to shapefile
campsites_sf <- campsites_pt %>%
  st_as_sf(coords = c("lat", "lon"))
```

```{r}
# Visually figuring out the forests that the campsites are in
forests <- macleish_layers[["forests"]] %>%
  rename(forest_type = Sheet1__Na)

leaflet() %>%
  addTiles() %>%
  addPolylines(data = macleish_layers[["boundary"]], weight = 1, color = "black") %>%
  addPolygons(data = forests, weight = 1, color = "green", popup = ~forest_type) %>%
  addMarkers(data = campsites_sf, popup = ~point)

# Create dataset that will only have those types of forests
pine_maple <- forests %>%
  filter(forest_type == "Old Field White Pine Forest" | forest_type == "Sugar Maple Forest")

# Some desirable forests to put campsites near (according to Reid)
oak <- forests %>%
  filter(forest_type == "Red Oak Forest" | forest_type == "Red Oak-Hemlock Forest" | forest_type == "Abandoned Pasture")
```

```{r}
# Create parking point
parking_pt <- tribble(
  ~point, ~lat, ~lon,
  "Parking Lot", -72.680663, 42.448013 
)

# Convert parking point to shapefile and set coordinate system
parking_sf <- parking_pt %>%
  st_as_sf(coords = c("lat", "lon")) %>%
  st_set_crs(4326)

# Create .5 mile buffer zone around parking lot (requirement)
parking_bf <- parking_sf %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 804.672) %>%
  st_transform(crs = 4326)

```

```{r}
# create streams buffer zones, 200 feet = 60.96 m (requirement)
streams_bf <- macleish_layers[["streams"]] %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 60.96) %>%
  st_transform(4326)

# create wetlands buffer zones (requirement)
wetlands_bf <- macleish_layers[["wetlands"]] %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 60.96) %>%
  st_transform(4326)

# create research buffer zones, 500 feet = 152.4 m (restriction)
research_bf <- macleish_layers[["research"]] %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

# create challenge course buffer zones (restriction)
challenge_bf <- macleish_layers[["challenge_courses"]] %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)
```

```{r}
# Our proposed campsites
our_camps_pt <- tribble(
  ~point, ~lat, ~lon,
  "Campsite A", -72.68207, 42.44893,
  "Campsite B", -72.67990, 42.44741
)
# Create campsite shapefile
our_camps_sf <- our_camps_pt %>%
  st_as_sf(coords = c("lat", "lon")) %>%
  st_set_crs(4326)

# Create buffer zones to show approx. campsite area (according to Reid)
our_camps_bf <- our_camps_sf %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 3) %>%
  st_transform(4326)
```


```{r}
#creating icons for proposed campsite, current campsite, and parking lot markers
icons <- awesomeIcons(icon = 'glyphicon glyphicon-tent', markerColor = 'orange')
ccicons <- awesomeIcons(icon = 'glyphicon glyphicon-tent', markerColor = 'blue')
caricon <- awesomeIcons(icon = "glyphicon glyphicon-road", markerColor = 'green')

# Make a leaflet map with green zones being our required areas and pink/red zones are our restricted areas
map <- leaflet() %>%
  addTiles() %>%
  # macleish boundary lines
  addPolylines(data = macleish_layers[["boundary"]], weight = 1, group = "Boundary") %>%
  # macleish streams
  addPolylines(data = macleish_layers[["streams"]], weight = 1, color = "blue", group = "Streams") %>%
  # contour lines
  addPolylines(data = macleish_layers[["contours_3m"]], weight = 1, color = "black", group = "Contours") %>%
  # macleish wetlands
  addPolygons(data = macleish_layers[["wetlands"]], color = "blue", opacity = 0.5, group = "Wetlands") %>%
  # draw stream buffer zones
  addPolygons(data = streams_bf, color = "lightgreen", fillColor = "transparent", group = "Streams") %>%
  # draw wetlands buffer zones
  addPolygons(data = wetlands_bf, color = "lightgreen", fillColor = "transparent", group = "Wetlands") %>%
  # draw research buffer zones
  addPolygons(data = research_bf, color = "pink", fillColor = "transparent", group = "Research Area") %>%
  # draw challenge course buffer zones
  addPolygons(data = challenge_bf, color = "pink", fillColor = "transparent", group = "Challenge Course") %>%
  # current campsite markers
  addAwesomeMarkers(data = campsites_sf, popup = ~point, icon = ccicons, group = "Campsites") %>%
  # current campsite forests
  addPolygons(data = pine_maple, weight = 1, color = "red", group = "Forests") %>%
  # good forests to be in (according to Reid)
  addPolygons(data = oak, weight = 1, color = "green", group = "Forests") %>%
  # macleish forests
  addPolygons(data = forests, weight = 1, color = "green", fillColor = "transparent", popup = ~forest_type) %>%
  addPolylines(data = macleish_layers[["trails"]], weight = 2, color = ~color, label = ~name) %>%
  # parking lot marker
  addAwesomeMarkers(data = parking_sf, icon = caricon, popup = ~point) %>%
  # draw parking lot buffer zone (0.5 mile radius)
  addPolygons(data = parking_bf, color = "green", fillColor = "transparent", group = "Parking") %>%
  # proposed campsite markers
  addAwesomeMarkers(data = our_camps_sf, popup = ~point, icon=icons, group = "Campsites") %>%
  # draw approximate size of campsite
  addPolygons(data = our_camps_bf, color = "orange", group = "Campsites") %>%
  # add map tool that will display coordinates of point that mouse is over
  addMouseCoordinates() %>%
#adding layer controls
  addLayersControl(overlayGroups = c("Boundary", "Streams", "Contours", "Wetlands", "Research Area", "Challenge Course", "Forests", "Parking", "Campsites"), options = layersControlOptions(collapsed = FALSE)) %>%
  addScaleBar()
map  
```


```{r}
# Map of attractions around the campsites
map2 <- leaflet() %>%
  addTiles() %>%
  # macleish boundary
  addPolylines(data = macleish_layers[["boundary"]], color = "black", weight = 1, opacity = 0.5, group = "Boundary") %>%
  # macleish streams
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 2, group = "Streams and Wetlands") %>%
  # macleish wetlands
  addPolygons(data = macleish_layers[["wetlands"]], weight = 2, group = "Streams and Wetlands") %>%
  # macleish forests
  addPolygons(data = forests, weight = 1, color = "transparent", fillColor = "transparent", popup = ~forest_type) %>%
  # macleish trails
  addPolylines(data = macleish_layers[["trails"]], weight = 2, color = ~color, label = ~name, group = "Trails") %>%
  # macleish landmarks
  addMarkers(data = macleish_layers[["landmarks"]], popup = ~Label, group = "Landmarks") %>%
  # parking lot marker
  addAwesomeMarkers(data = parking_sf, popup = ~point, icon = caricon, group = "Parking Lot") %>%
  addScaleBar()%>%
  # proposed campsite markers
  addAwesomeMarkers(data = our_camps_sf, popup = ~point, icon=icons, group = "Campsites") %>%
  # draw approximate size of campsite
  addPolygons(data = our_camps_bf, color = "orange", group = "Campsites")%>%
  addAwesomeMarkers(data = campsites_sf, popup = ~point, icon = ccicons, group = "Campsites") %>%
  #adding layer controls
  addLayersControl(overlayGroups = c("Boundary", "Streams and Wetlands", "Trails", "Landmarks", "Parking Lot", "Campsites"), options = layersControlOptions(collapsed = FALSE)) 

map2
```

Writeup: 

Problem statement: The purpose of our project was to find at least two feasible locations for new campsites in Macleish. To do so, we closely adhered to the given requirements and chose only locations that fit. 
Visual mapping: The second map was for us to select potential campsite points by plotting all of the given requirements. We used green circles around the rivers and wetlands to denote zones that fit the water requirement, a single green circle for the parking lot zone, and also green polygons for forests that we thought were good to build a campsite on. To denote areas that we should avoid, we used pink circles for the research and challenge points and red polygons for the forest types that we already had campsites in. For the proposed campsites, we changed the markers to orange with tent icons to differentiate them from the other points we had. In the third map, which is an "aesthetic" map for visitors to consult when choosing their campsite, we used the given colors in the dataset for the trails and kept the campsite markers as is, while adding in additional landmarks so visitors could see where they wanted to go in Macleish. The original campsites are part of the landmarks.
Description of data: For the contour data, we used the 3m data in the Macleish package. We already knew that with contour lines, the farther apart they are the flatter the slope of the area, so we used this knowledge to help determine a "relatively flat" campsite. We also talked to Bertone-Johnson about the forest types that he would prefer. He said that sugar maple or oak forests were fairly good, possibly abandoned pasture but that would have to be determined on-site, and not near wetlands, vernal pools, or "old field" forests. He also gave us leeway on the parking lot requirement, as he said that it just had to be within 0.5 miles of the parking lot. We decided that based on common sense, the campsite should not be right next to major roads. 
Recommendations: After reviewing all of the project requirements, our first campsite A is right on the West Loop trail in a red oak forest near a river within the Macleish boundary. The second campsite B we propose is next to the East Loop trail in abandoned pasture near the same river as site A. We also included buffer zones of 3m as the average campsite size. While two of us have been camping before, we can only guess at the practical elements of this project. If Smith wants to build a campsite, it will have to clear trees in the area and perhaps level the ground so tents can be set up. Then they will have to pay logging and landscaping contractors for several weeks at most given the small size of the campsites. Building new sites will cause an immediate loss in plants and habitat for wildlife, but people using the campsites may also disturb areas around the sites and the usual problems with litter, soil compaction, etc. Some roadblocks that might come up are transportation of building materials or how to integrate the campsites with the trails, but the first concern is partially solved by the parking lot being near both sites.

